\documentclass{article}
\usepackage[a4paper, margin=3mm, landscape]{geometry}
\usepackage{multicol}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{listings}
\usepackage{soul}

\pdfinfo{
  /Title (ST2334.pdf)
  /Creator (TeX)
  /Producer (pdfTeX 1.40.0)
  /Author (Jason Qiu)
  /Subject (ST2334)
  /Keywords (ST2334, nus, cheatsheet,pdf)
}

\pagestyle{empty}
\setcounter{secnumdepth}{0}
\setlength{\columnseprule}{0.25pt}

% Redefine section commands to use less space
\makeatletter
\renewcommand{\section}{\@startsection{section}{1}{0mm}%
  {-1ex plus -.5ex minus -.2ex}%
  {0.5ex plus .2ex}%x
{\normalfont\large\bfseries}}
\renewcommand{\subsection}{\@startsection{subsection}{2}{0mm}%
  {-1explus -.5ex minus -.2ex}%
  {0.5ex plus .2ex}%
{\normalfont\normalsize\bfseries}}
\renewcommand{\subsubsection}{\@startsection{subsubsection}{3}{0mm}%
  {-1ex plus -.5ex minus -.2ex}%
  {1ex plus .2ex}%
{\normalfont\small\bfseries}}%
\makeatother

% Adjust spacing for all itemize/enumerate
\setlength{\leftmargini}{0.5cm}
\setlength{\leftmarginii}{0.5cm}
\setlist[itemize,1]{leftmargin=2mm,labelindent=1mm,labelsep=1mm}
\setlist[itemize,2]{leftmargin=2mm,labelindent=1mm,labelsep=1mm,label=$\bullet$}

% Font
\renewcommand{\familydefault}{\sfdefault}

% Define colors for math formulas
\definecolor{myblue}{cmyk}{1,.72,0,.38}
\everymath\expandafter{\the\everymath \color{myblue}}

% Custom command for keywords
\definecolor{highlight}{RGB}{251,243,218}
\newcommand{\keyword}[2][]{\sethlcolor{highlight}\hl{\textbf{#2}} #1 - }
\newcommand{\ilkeyword}[1]{\sethlcolor{highlight}\hl{\textbf{#1}}}

% Define colors and style for code
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codered}{HTML}{CC241D}
\definecolor{backcolor}{rgb}{0.95,0.95,0.95}
\lstdefinestyle{codestyle}{
  backgroundcolor = \color{backcolor},
  commentstyle = \color{codegray},
  keywordstyle = \color{codered},
  stringstyle = \color{codegreen},
  basicstyle = \ttfamily,
  breakatwhitespace = false,
  showstringspaces = false,
  breaklines = true,
  showtabs = false,
  tabsize = 2
}
\lstset{style = codestyle}

% -----------------------------------------------------------------------
\begin{document}
\begin{multicols*}{3}
\footnotesize

% Title box
\begin{center}
  \fbox{
    \parbox{0.8\linewidth}{
      \centering \textcolor{black}{
        {\Large\textbf{ST2334}} \\
        \normalsize{AY22/23 Sem 1}} \\
        {\footnotesize \textcolor{gray}{github.com/jasonqiu212}}
    }
  }
\end{center}

\section{01. Basic Concepts of Probability}

\subsection{Event Operations}

\begin{itemize}
  \item \keyword{Mututally Exclusive}{$A \cap B = \emptyset$}
  \item \keyword{Contained}{$A \subset B$}
  \item \keyword{Equivalence}{$A \subset B$ and $A \supset B \rightarrow A = B$}
  \item \keyword{Distributive}{$A \cap (B \cup C) = (A \cup B) \cup (A \cup C)$}
  \item \keyword{DeMorgan's}{$(A \cup B)' = A' \cap B'$}
  \item $A = (A \cap B) \cup (A \cap B')$
\end{itemize}

\subsection{Counting Methods}

\begin{itemize}
  \item \keyword{Multiplcation Principle}{Given r experiments performed \textbf{sequentially} and each has $n_1, n_2, ..., n_r$ outcomes. After r experiments, there are $n_1 n_2 ... n_r$ outcomes.}
  \item \keyword{Addition Principle}{Given experiment can be done in k different ways and each has $n_1, n_2, ..., n_r$ ways. There are $n_1 + n_2 + ... + n_k$ total ways.}
  \item \keyword{Permutation}{$_{n}P_{r} = \frac{n!}{(n-r)!}$}
  \item \keyword{Combination}{$\binom{n}{r} = \frac{n!}{(n-r)!r!}$}
\end{itemize}

\subsection{Probability}

\subsubsection{Axioms of Probability}
\begin{enumerate}
    \item For any event A, $0 \leq P(A) \leq 1$
    \item P(S) = 1
    \item If $A \cap B = \emptyset$, then $P(A \cup B) = P(A) + P(B)$
\end{enumerate}
\begin{itemize}
  \item $P(A') = 1 - P(A)$
  \item $P(A) = P(A \cap B) + P(A \cap B')$
  \item $P(A \cup B) = P(A) + P(B) - P(A \cap B)$
  \item If $A \subset B$, then $P(A) < P(B)$
\end{itemize}

\subsection{Finite Sample Space with Equally Likely Outcomes}

Given sample space $S = \{a_1, ..., a_k\}$ and all outcomes are \textbf{equally likely}, i.e. $P(a_1) = ... = P(a_k)$:
\[\text{For any event } A \subset S, P(A) = \frac{\text{No. of sample points in A}}{\text{No. of sample points in S}}\]

\subsection{Conditional Probability}

\[P(B|A) = \frac{P(B \cap A)}{P(A)} = \frac{P(A|B)P(B)}{P(A)}\]

\subsection{Independence}

\begin{itemize}
    \item $A \perp B \leftrightarrow P(A \cap B) = P(A)P(B)$
    \item $A \perp B \leftrightarrow P(A|B) = P(A)$
\end{itemize}

\subsection{Law of Total Probability}

\begin{itemize}
    \item \keyword{Partition}{If $A_1, ..., A_n$ are mutually exclusive events and $\bigcup _{i=1} ^{n} A_i = S$, then $A_1, ..., A_n$ are partitions}
    \item If $A_1, ..., A_n$ are partitions of S, then for any event B:
    \[P(B) = \sum _{i=1} ^{n} P(B \cap A_i) = \sum _{i=1} ^{n} P(B|A_i)P(A_i)\]
\end{itemize}

\subsection{Bayes' Theorem}

Let $A_1, ..., A_n$ be partitions of S. For any event B:
\[P(A_k|B) = \frac{P(B|A_k)P(A_k)}{\sum _{i=1} ^{n} P(B|A_k)P(A_i)}\]

\section{02. Random Variables}

\begin{itemize}
    \item Motivation: Assign value to outcome of experiment
    \item \keyword{Random Variable}{Let S be sample space. Function X which maps $\mathbb{R}$ to every $s \in S$}
\end{itemize}

\subsection{Probability Distribution}

\begin{itemize}
    \item Probability assigned to each possible $X$
    \item Given RV $X$ with range of $R_x$:
      \subitem \keyword{Discrete}{Numbers in $R_x$ are finite or countable}
      \subitem \keyword{Continuous}{$R_x$ is interval}
\end{itemize}

\subsubsection{Discrete Probability Distribution}
\begin{itemize}
    \item \keyword{Probability Function}{Given $R_x = \{x_1, ...\}$. For each $x_i$, there's some probability that $X = x_i$:}
    \[f(x) = P(X = x)\]
    \item $p.f.$ must satisfy:
        \begin{enumerate}
            \item $f(x_i) = P(X = x_i)$ for $x_i \in R_x$
            \item $f(x_i) = 0$ for $x_i \notin R_x$
            \item $\sum _{i=1} ^{\infty} f(x_i) = 1$
            \item $\forall B \subseteq \mathbb{R}, P(X \in B) = \sum _{x_i \in B \cap R_x} f(x_i)$
        \end{enumerate}
    \item \keyword{Probability Distribution}{Collection of pairs $(x_i, f(x_i))$}
\end{itemize}

\subsubsection{Continuous Probability Distribution}
\begin{itemize}
    \item \keyword{Probability Function}{Given $R_x$ is interval. Quantifies probability that $X$ is in some range.}
    \item $p.f.$ must satisfy:
        \begin{enumerate}
            \item $f(x) \geq 0$
            \item $f(x) = 0$ for $x \notin R_x$
            \item $\int _{R_x} f(x) dx = 1$
            \item $\forall a,b \text{ s.t. } a \leq b, P(a \leq X \leq b) = \int _{a} ^{b} f(x) dx$
        \end{enumerate}
    \item Note: $P(X = x_0) = \int _{x_0} ^{x_0} f(x) dx = 0$
\end{itemize}

\subsection{Cumulative Distributive Function}

Given RV $X$, which can be discrete or continuous:
\[F(x) = P(X \leq x)\]

\begin{itemize}
    \item $F(x)$ is non-decreasing and $0 \leq F(x) \leq 1$
    \item \textbf{For discrete RV}: Step function
    \[F(x) = \sum _{t \in R_x; t \leq x} f(t)\]
    \begin{itemize}
        \item $P(a \leq X \leq b) = F(b) - \lim _{x \to a^-} F(x)$
        \item $0 \leq f(x) \leq 1$
    \end{itemize}

    \item \textbf{For continuous RV}:
    \[F(x) = \int _{-\infty} ^{x} f(t) dt\]
    \[f(x) = \frac{d(F(x))}{dx}\]
    \begin{itemize}
        \item $P(a \leq X \leq b) = P(a < X < b) = F(b) - F(a)$
        \item $0 \leq f(x)$ e.g. $f(x) = 3x^2$ is a valid $p.f.$ since $\int _{R_x} f(x) dx = 1$
    \end{itemize}
\end{itemize}

\subsection{Expectation of Random Variable}

\begin{itemize}
    \item \textbf{Mean of discrete RV}: 
    \[\mu = E(X) = \sum _{x \in R_x} x_i f(x_i) = \sum _{i=1} ^{\infty} P(X \geq i)\]
    \begin{itemize}
        \item Let $g$ be some function. $E(g(x)) = \sum _{x \in R_x} g(x)f(x)$
    \end{itemize}
    \item \textbf{Mean of continuous RV}: 
    \[\mu = E(X) = \int _{x \in R_x} x f(x) dx\]
    \begin{itemize}
        \item Let $g$ be some function. $E(g(x)) = \int _{x \in R_x} g(x)f(x)dx$
    \end{itemize}
    \item $E(aX + b) = aE(X) + b$
    \item Linearity of expectation: $E(X + Y) = E(X) + E(Y)$
\end{itemize}

\subsection{Variance of Random Variable}

\[\sigma_X^2 = V(X) = E((X - \mu_X)^2)\]

\begin{itemize}
    \item \textbf{Variance of discrete RV}: 
    \[V(X) = \sum _{x \in R_x} (x - \mu_X)^2 f(x)\]
    \item \textbf{Variance of continuous RV}: 
    \[V(X) = \int _{x \in R_x} (x - \mu_X)^2 f(x) dx\]
    \item $V(X) = 0$ when $X$ is a constant
    \item $V(aX+b) = a^2V(X)$
    \item $V(X) = E(X^2) - (E(X))^2$
    \item \keyword{Standard Deviation}{$\sigma_X = \sqrt{V(X)}$}
\end{itemize}

\section{03. Joint Distributions}

\section{04. Special Probability Distributions}

\subsection{Discrete Uniform Distribution}

\begin{itemize}
  \item If $X$ has values $x_1, x_2, ..., x_k$ with \textbf{equal probability}
  \item p.f.: $f_X(x) = \frac{1}{k}$ where $x = x_1, ..., x_k$ and $0$ otherwise
  \item Expectation: $\mu_X = E(X) = \sum_{i = 1} ^{k} x_i f_X (x_i) = \frac{1}{k} \sum_{i=1} ^{k} x_i$
  \item Variance: $\sigma_X^2 = V(X) = E(X^2) - (E(X))^2 = \frac{1}{k} \sum_{i=1} ^{k} x_i^2 - \mu_X^2$
\end{itemize}

\subsection{Bernoulli}

\begin{itemize}
  \item \keyword{Bernoulli Trial}{Random experiment with 2 possible outcomes (success and failure)}
\end{itemize}

\subsubsection{Bernoulli Random Variable}
\begin{itemize}
  \item Number of successes in Bernoulli trial (Either 1 or 0)
  \item Let $0 \leq p \leq 1$ be the probability of success in Bernoulli trial
  \[ f_X (x) = P(X = x) = 
  \begin{cases}
    p & x = 1\\
    1 - p & x = 0\\
    0 & otherwise
  \end{cases}
    \]
  \item $f_X (x) = p^x (1-p)^{1-x}$ for $x=0$ or $1$
  \item Notation: $X \sim Ber(p)$ and $q = 1 - p$
  \item $\mu_X = E(X) = p$ and $\sigma_X^2 = V(X) = p(1-p)$
\end{itemize}

\subsubsection{Bernoulli Process}
\begin{itemize}
  \item Sequence of repeatedly performed \textbf{independent and identical} Ber. trials
  \item Generates sequence of \textbf{independet and identically distributed (i.i.d.)} Ber. RVs: $X_1, X_2, ...$
\end{itemize}

\subsection{Binomial Distribution}

\begin{itemize}
  \item \keyword{Binomial RV}{Counts the number of successes in n trials in a Ber. process}
  \item Given n trials with each trial having probability p of success: 
  \[P(X = x) = \binom{n}{x} p^x (1-p)^{n-x}\]
  \item Notation: $X \sim B(n, p)$
  \item $E(X) = np$ and $V(X) = np(1-p)$
\end{itemize}

\subsection{Negative Binomial Distribution}

\begin{itemize}
  \item Let X = Number of i.i.d. Bernoulli(p) trials until kth success occurs
  \[P(X = x) = \binom{x-1}{k-1} p^k (1-p)^{x-k}\]
  \item Notation: $X \sim NB(k, p)$
  \item $E(X) = \frac{1}{p}$ and $V(X) = \frac{(1-p)}{p^2}$
\end{itemize}

\subsubsection{Geometric Distribution}
\begin{itemize}
  \item Let X = Number of i.i.d. Bernoulli(p) trials until 1st success occurs
  \[
    P(X = x) = p (1-p)^{x-1}
  \]
  \item Notation: $X \sim G(p)$
  \item $E(X) = \frac{1}{p}$ and $V(X) = \frac{1-p}{p^2}$
\end{itemize}

\subsection{Poisson Distribution}
\begin{itemize}
  \item \keyword{Poisson RV}{Denotes number of events happening in \textbf{fixed period of time}}
  \[
    P(X = k) = \frac{e^{-\lambda}\lambda^k}{k!}
  \]
  \item Notation: $X \sim Poisson(\lambda)$ where $\lambda > 0$ is expected number of occurences during some period
  \item $E(X) = \lambda$ and $V(X) = \lambda$
  \item \keyword{Poisson Process}{Continuous time process, where we count number of correucesn within some internval of time}
\end{itemize}

\end{multicols*}
\end{document}
