\documentclass{article}
\usepackage[a4paper, margin=3mm, landscape]{geometry}
\usepackage{multicol}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{listings}
\usepackage{soul}
\usepackage{graphicx}

\pdfinfo{
    /Title (CS3219.pdf)
    /Creator (TeX)
    /Producer (pdfTeX 1.40.0)
    /Author (Jason Qiu)
    /Subject (CS3219)
    /Keywords (CS3219, nus, cheatsheet, pdf)
}

\graphicspath{ {./img/} }

\pagestyle{empty}
\setcounter{secnumdepth}{0}
\setlength{\columnseprule}{0.25pt}

% Redefine section commands to use less space
\makeatletter
\renewcommand{\section}{\@startsection{section}{1}{0mm}%
    {-1ex plus -.5ex minus -.2ex}%
    {0.5ex plus .2ex}%x
{\normalfont\large\bfseries}}
\renewcommand{\subsection}{\@startsection{subsection}{2}{0mm}%
    {-1explus -.5ex minus -.2ex}%
    {0.5ex plus .2ex}%
{\normalfont\normalsize\bfseries}}
\renewcommand{\subsubsection}{\@startsection{subsubsection}{3}{0mm}%
    {-1ex plus -.5ex minus -.2ex}%
    {1ex plus .2ex}%
{\normalfont\small\bfseries}}%
\makeatother

% Adjust spacing for all itemize/enumerate
\setlength{\leftmargini}{0.5cm}
\setlength{\leftmarginii}{0.5cm}
\setlist[itemize,1]{leftmargin=2mm,labelindent=1mm,labelsep=1mm}
\setlist[itemize,2]{leftmargin=2mm,labelindent=1mm,labelsep=1mm,label=$\bullet$}

% Font
\renewcommand{\familydefault}{\sfdefault}

% Define colors for math formulas
\definecolor{myblue}{cmyk}{1,.72,0,.38}
\everymath\expandafter{\the\everymath \color{myblue}}

% Custom command for keywords
\definecolor{highlight}{RGB}{251,243,218}
\newcommand{\keyword}[2]{\sethlcolor{highlight}\hl{\textbf{#1}} - #2}
\newcommand{\ilkeyword}[1]{\sethlcolor{highlight}\hl{\textbf{#1}}}

% Custom command for partial derivatives
\newcommand{\partialderivative}[2][]{\frac{\partial #1}{\partial #2}}

% Define colors and style for code
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codered}{HTML}{CC241D}
\definecolor{backcolor}{rgb}{0.95,0.95,0.95}
\lstdefinestyle{codestyle}{
    backgroundcolor = \color{backcolor},
    commentstyle = \color{codegray},
    keywordstyle = \color{codered},
    stringstyle = \color{codegreen},
    basicstyle = \ttfamily,
    breakatwhitespace = false,
    showstringspaces = false,
    breaklines = true,
    showtabs = false,
    tabsize = 2
}
\lstset{style = codestyle}

% -----------------------------------------------------------------------
\begin{document}
\begin{multicols*}{4}
\footnotesize

% Title box
\begin{center}
    \fbox{
        \parbox{0.8\linewidth}{
            \centering \textcolor{black}{
                {\Large\textbf{CS3219}} \\
                \normalsize{AY24/25 Sem 1}} \\
                {\footnotesize \textcolor{gray}{github.com/jasonqiu212}}
        }
    }
\end{center}

\section{01. Introduction}

\subsection{Software Types}

\begin{itemize}
    \item \keyword{Edge Computing}{Computation done at leaf nodes}
    \item \keyword{Cloud Computing}{Host software on ext. data center}
    \begin{itemize}
        \item \keyword{Cloud-enabled}{Legacy applications modified to run on the cloud (vs. cloud-native)}
    \end{itemize}
\end{itemize}

\subsection{Software Development Process}

\begin{itemize}
    \item \keyword{Waterfall}{Sequential approach good for stable req.}
    \item \keyword{Agile}{Iterative development with feedback loops and quick responses to changes}
    \begin{itemize}
        \item \keyword{Scrum}{Work done in sprints, where a subset of the product backlog is cleared}
    \end{itemize}
\end{itemize}

\subsection{Software Delivery}

\begin{itemize}
    \item \keyword{Deployment}{Make software available to use after dev.}
    \begin{itemize}
        \item Bare metal: Customized build for target platforms
        \item Virtual machine: Use VM to run guest OS to run app.
        \item Containers: Include only necessary OS processes and dependencies (Lighter than VM)
        \item Serverless: Cloud-native servers that don't need developers to manage (Let provider manage resources)
    \end{itemize}
    \keyword{DevOps}{Practices combining software dev. and ops.}
    \begin{itemize}
        \item Purpose: Reduce time between committing change to the change reaching production while ensuring quality
        \item \keyword{Cont. Integration}{Auto build, unit test, deploy to staging, and acceptance test, to show problems early}
        \item \keyword{Continuous Delivery}{Same as above, except with manual deployment to production. Ensures that every good build is
        potentially ready for production release.}
        \item \keyword{Continuous Deployment}{Same as above, but with auto deployment to production}
    \end{itemize}
\end{itemize}

\section{02. Requirements}

\end{multicols*}
\end{document}
