\documentclass{article}
\usepackage[a4paper, margin=3mm, landscape]{geometry}
\usepackage{multicol}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{listings}
\usepackage{soul}
\usepackage{graphicx}

\pdfinfo{
    /Title (CS2109S.pdf)
    /Creator (TeX)
    /Producer (pdfTeX 1.40.0)
    /Author (Jason Qiu)
    /Subject (CS2109S)
    /Keywords (CS2109S, nus, cheatsheet, pdf)
}

\graphicspath{ {./img/} }

\pagestyle{empty}
\setcounter{secnumdepth}{0}
\setlength{\columnseprule}{0.25pt}

% Redefine section commands to use less space
\makeatletter
\renewcommand{\section}{\@startsection{section}{1}{0mm}%
    {-1ex plus -.5ex minus -.2ex}%
    {0.5ex plus .2ex}%x
{\normalfont\large\bfseries}}
\renewcommand{\subsection}{\@startsection{subsection}{2}{0mm}%
    {-1explus -.5ex minus -.2ex}%
    {0.5ex plus .2ex}%
{\normalfont\normalsize\bfseries}}
\renewcommand{\subsubsection}{\@startsection{subsubsection}{3}{0mm}%
    {-1ex plus -.5ex minus -.2ex}%
    {1ex plus .2ex}%
{\normalfont\small\bfseries}}%
\makeatother

% Adjust spacing for all itemize/enumerate
\setlength{\leftmargini}{0.5cm}
\setlength{\leftmarginii}{0.5cm}
\setlist[itemize,1]{leftmargin=2mm,labelindent=1mm,labelsep=1mm}
\setlist[itemize,2]{leftmargin=2mm,labelindent=1mm,labelsep=1mm,label=$\bullet$}

% Font
\renewcommand{\familydefault}{\sfdefault}

% Define colors for math formulas
\definecolor{myblue}{cmyk}{1,.72,0,.38}
\everymath\expandafter{\the\everymath \color{myblue}}

% Custom command for keywords
\definecolor{highlight}{RGB}{251,243,218}
\newcommand{\keyword}[2][]{\sethlcolor{highlight}\hl{\textbf{#2}} #1 - }
\newcommand{\ilkeyword}[1]{\sethlcolor{highlight}\hl{\textbf{#1}}}

% Define colors and style for code
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codered}{HTML}{CC241D}
\definecolor{backcolor}{rgb}{0.95,0.95,0.95}
\lstdefinestyle{codestyle}{
    backgroundcolor = \color{backcolor},
    commentstyle = \color{codegray},
    keywordstyle = \color{codered},
    stringstyle = \color{codegreen},
    basicstyle = \ttfamily,
    breakatwhitespace = false,
    showstringspaces = false,
    breaklines = true,
    showtabs = false,
    tabsize = 2
}
\lstset{style = codestyle}

% -----------------------------------------------------------------------
\begin{document}
\begin{multicols*}{3}
\footnotesize

% Title box
\begin{center}
    \fbox{
        \parbox{0.8\linewidth}{
            \centering \textcolor{black}{
                {\Large\textbf{CS2109S}} \\
                \normalsize{AY22/23 Sem 2}} \\
                {\footnotesize \textcolor{gray}{github.com/jasonqiu212}}
        }
    }
\end{center}

\section{01. Introduction}

\begin{itemize}
    \item \keyword{Agent}{Anything that can perceive its environment through sensors and acting upon that env. through actuators}
    \item \keyword{Agent Function}{Maps from percept histories to actions}
    \item \keyword{Rational Agent}{Chooses an action that is expected to maximize its performance measure, given by percept sequence and built-in knowledge}
    \item \keyword{Autonomous Agent}{If behavior is determined by its own expereince}
\end{itemize}

\subsection{Performance Measure of Function}

\begin{itemize}
    \item Motivation: For an agent to do the right thing, need a measure of goodness
    \item Performance vs. Cost
\end{itemize}


\begin{enumerate}
    \item Best for whom?
    \item What are we optimizing?
    \item What information is available?
    \item What are the side effects and costs?
\end{enumerate}

\subsection{Defining the Problem: PEAS}

\begin{enumerate}
    \item Performance measure
    \item Environment
    \item Actuators
    \item Sensors
\end{enumerate}

\subsection{Characterizing the Environment}

\begin{enumerate}
    \item \keyword{Fully observable}{(vs. Partially) Agent's sensors can access complete state of env. all the time}
    \item \keyword{Deterministic}{(vs. Stochastic) Next state of env. is determined by \textbf{current state} and \textbf{action executed by agent}}
    \begin{itemize}
        \item \keyword{Strategic}{If env. is deterministic except for actions of other agents}
    \end{itemize}
    \item \keyword{Episodic}{(vs. Sequential) Agent's experience is divided into atomic \textbf{episodes}, where each episode includes perceiving and an action, and \textbf{action depends on episode} itself}
    \item \keyword{Static}{(vs. Dynamic) Env. is unchanged while agent is deciding}
    \begin{itemize}
        \item \keyword{Semi}{Time does not affect env., but affects performance score}
    \end{itemize}
    \item \keyword{Discrete}{(vs. Continuous) Discrete num. of percepts and actions}
    \item \keyword{Single Agent}{(vs. Multi-agent) Agent operating by itself in an env.}
\end{enumerate}

\subsection{Implementing Agents (in ascending complexity)}

\begin{enumerate}
    \item \keyword{Simple Reflex Agents}{Fixed conditional rules}
    \item \keyword{Model-based Reflex Agents}{Stores percept history to make decisions about internal model of world with conditional rules. Eg. Roomba}
    \item \keyword{Goal-based Agents}{Keep in mind a goal and action aims to achieve it}
    \item \keyword{Utility-based Agents}{Find best way to achieve goal}
    \item \keyword{Learning Agents}{Learn from previous experiences}
\end{enumerate}

\subsection{Exploitation vs. Exploration}

\begin{itemize}
    \item \keyword{Exploitation}{Maximize expected utility using current knowledge of world}
    \item \keyword{Exploration}{Learn more about the world to improve future gains. May not always maximize performance measure.}
\end{itemize}

\section{02. Searching}

\begin{itemize}
    \item Deterministic, fully observable
    \item \keyword{Tree Search}{Can revisit nodes}
    \item \keyword{Graph Search}{Tracks visited (Tree Search + Memoization)}
    \item \keyword{Uninformed Search}{Uses only information available in problem definition}
\end{itemize}

\subsection{Formulating the Problem}

\begin{enumerate}
    \item How to represent state in problem?
    \item Initial state
    \item Actions: Successor function
    \item Goal test
    \item Path cost
\end{enumerate}

\begin{itemize}
    \item \keyword{Abstraction Function}{Maps abstracted representation to real world state}
    \item \keyword{Representation Invariant}{$I(c) = \textbf{True} \rightarrow \exists a \textbf{ s.t. } AF(c) = a$}
\end{itemize}

\subsection{Breadth-first Search}

\begin{itemize}
    \item Idea: Expand shallowest unexpanded node using \textbf{queue}
    \item Given: $b$: Branching factor and $d$: Depth of optimal solution
    \item Complete: Yes (if tree is finite)
    \item Time: $O(b^{d+1})$
    \item Space: $O(b^d)$
    \item Optimal: Yes (if cost = 1)
    \item BFS is Uniform-cost Search with same cost
\end{itemize}

\subsection{Uniform-cost Search}

\begin{itemize}
    \item Idea: Expand least-cost unexpanded node using \textbf{priority queue} (Dijkstra's)
    \item Given: $C^*$: Cost of optimal solution
    \item Complete: Yes (if step cost $\geq \epsilon$ where $\epsilon \geq 0$)
    \item Time: $O(b^{(C^* / \epsilon)})$ ($C^* / \epsilon$ is approx. number of layers)
    \item Space: $O(b^{(C^* / \epsilon)})$
    \item Optimal: Yes
\end{itemize}

\subsection{Depth-first Search}

\begin{itemize}
    \item Idea: Expand deepest unexpanded node using \textbf{stack}
    \item Given: $m$: Maximum depth of tree
    \item Complete: No (fails with infinite depth or loops)
    \item Time: $O(b^m)$
    \item Space: $O(bm)$ (better than BFS)
    \item Optimal: No
\end{itemize}

\subsection{Depth-limited Search}

\begin{itemize}
    \item DFS with depth limit $I$ where nodes at depth $I$ have no children
    \item Time: $b^0 + b^1 + ... + b^{(d - 1)} + b^d = O(b^d)$
\end{itemize}

\subsection{Iterative Deepening Search}

\begin{itemize}
    \item Idea: Try different depths for depth-limited search
    \item Complete: Yes
    \item Time: $(d + 1)b^0 + db^1 + ... + b^d = O(b^d)$ (More overhead than DLS)
    \item Space: $O(bd)$
\end{itemize}

\subsection{Summary}

\begin{tabular}{ |c|c|c|c|c|c| }
    \hline
    & \textbf{BFS} & \textbf{Uniform Cost} & \textbf{DFS} & \textbf{DLS} & \textbf{IDS} \\
    \hline
    \textbf{Complete} & Yes & Yes & No & No & Yes \\
    \hline
    \textbf{Time} & $O(b^d)$ & $O(b^{C^* / \epsilon})$ & $O(b^m)$ & $O(b^l)$ & $O(b^d)$ \\
    \hline
    \textbf{Space} & $O(b^d)$ & $O(b^{C^* / \epsilon})$ & $O(bm)$ & $O(bl)$ & $O(bd)$ \\
    \hline
    \textbf{Optimal} & Yes & Yes & No & No & No \\
    \hline
\end{tabular}

\subsection{Bidirectional Search}

\begin{itemize}
    \item Idea: Search both forwards from initial state and backwards from goal state. Stop when searches meet.
    \item Time: $O(2 b^{d/2})$
    \item Operators must be reversible
    \item Can have many goal states
    \item How to check if node intersects with other half?
\end{itemize}

\end{multicols*}
\end{document}
